---
title: "resids_loo"
output: html_document
---

# Taken from Peter S
# Load Data
```{r setup, include=FALSE}
#knitr::opts_chunk$set(echo = TRUE, tidy = TRUE, tidy.opts = list(width.cutoff = 60))

knitr::opts_chunk$set(message=FALSE, warning=FALSE, fig.align="center",
               echo=FALSE)
```

```{r}
library(dplyr)
library(ggrepel)
library(stargazer)
library(tidyverse)
library(ggplot2)
library(tidyr)

library(bestglm)
library(stargazer)
library(car)
```

```{r}

```


# First Analysis 

## What are the different county variables that effect the conviction rates of different defendant types 
```{r}
rdf<-read.csv("../../Data/county_characteristics_conviction.csv")

rdf <- rdf %>% 
  mutate(Log.pop = log(Population),
         Log.urban = log(Urban.Population+1),
         Log.rural = log(Rural.Population+1))

rdf_PA <- rdf %>% 
  filter(state == "PA")
  
  
rdf_OR <- rdf %>% 
  filter(state == "OR")
  
rdf_FL <-rdf %>% 
  filter(state == "FL")

#names(rdf_PA)

#max(car::logit(rdf_PA$Public.Defender.conviction.rate))
```


# Population
Log.pop
Log.urban
#Log.rural <- correlated with urban
Young.Males.Population
Largest.Municipality.Population
High.School.Graduates

# Racial/Ethnicity
White.Population <- baseline
African.American.Population
Native.American.Alaskan.Population
Asian.or.Pacific.Islander.Population
# Other.Race.Population <- sum to 1 so remove basline
Hispanic.or.Latino.Population

# Econ
#Single.Female.Headed.Households.with.Children
Unemployment.Rate
#Non.Citizens                                      
Below.Poverty.Line
Median.Household.Income                          
#Average.Commute.Minutes
#Residential.Mobility

# Crim Justice
Number.of.Criminal.Court.Judges
Police.Officers.per.100.000.Residents
# Law.Enforcement.Agencies.Reporting.to.UCR
# Total.Number.of.Law.Enforcement.Agencies <- tied to county size, population
Number.of.Full.Time.Prosecutors
#Number.of.Full.Time.Sworn.Law.Enforcement.Officers < correlated with # full-time prosecutors, scales with pop
# Number.of.Part.Time.Prosecutors

```{r, eval = FALSE}
mod <- lm(
  car::logit(Public.Defender.conviction.rate) ~ 
    # Population
    Log.pop + Log.urban + Young.Males.Population + Largest.Municipality.Population + High.School.Graduates +
    # Racial/Ethnicity
    White.Population + African.American.Population + Native.American.Alaskan.Population + 
    Asian.or.Pacific.Islander.Population + Hispanic.or.Latino.Population +
    # Econ
    Below.Poverty.Line + Unemployment.Rate + Median.Household.Income +
    # Criminal Justice
    Number.of.Criminal.Court.Judges + Police.Officers.per.100.000.Residents + Number.of.Full.Time.Prosecutors, 
  data   = rdf_PA,
  na.action = na.omit)
#summary(mod)
vif(mod)

###### VIF IS REALLY HIGH #########
# VIF < 5 → fine
# VIF 5–10 → borderline
# VIF > 10 → drop or rethink


# We remove White.Population and Median.Household.Income
mod1 <- lm(
  car::logit(Public.Defender.conviction.rate) ~ 
    # Population
    Log.pop + Log.urban + Young.Males.Population + Largest.Municipality.Population + High.School.Graduates +
    # Racial/Ethnicity
    African.American.Population + Native.American.Alaskan.Population + 
    Asian.or.Pacific.Islander.Population + Hispanic.or.Latino.Population +
    # Econ
    Below.Poverty.Line + Unemployment.Rate + #Median.Household.Income +
    # Criminal Justice
    Number.of.Criminal.Court.Judges + Police.Officers.per.100.000.Residents + Number.of.Full.Time.Prosecutors, 
  data   = rdf_PA,
  na.action = na.omit)
#summary(mod)
vif(mod1)


# Better but not quite
# We remove Log.urban as it drops the VIP of Log.pop the most (vs Largest.Municipality.Population)
mod2 <- lm(
  car::logit(Public.Defender.conviction.rate) ~ 
    # Population
    Log.pop + Young.Males.Population + Largest.Municipality.Population + #High.School.Graduates +
    # Racial/Ethnicity
    African.American.Population + Native.American.Alaskan.Population + 
    Asian.or.Pacific.Islander.Population + Hispanic.or.Latino.Population +
    # Econ
    Below.Poverty.Line + Unemployment.Rate +
    # Criminal Justice
    Number.of.Criminal.Court.Judges + Police.Officers.per.100.000.Residents + Number.of.Full.Time.Prosecutors, 
  data   = rdf_PA,
  na.action = na.omit)
#summary(mod)
vif(mod2)

# Police.Officers.per.100.000.Residents 
# Note moderate multicollinearity
# It represents a different concept (law enforcement capacity) so we leave it


```
```{r, eval = FALSE}
# FL 
mod3 <- lm(
  car::logit(Public.Defender.conviction.rate) ~ 
    # Population
    Log.pop + Young.Males.Population + Largest.Municipality.Population + #High.School.Graduates +
    # Racial/Ethnicity
    African.American.Population + Native.American.Alaskan.Population + 
    Asian.or.Pacific.Islander.Population + Hispanic.or.Latino.Population +
    # Econ
    Below.Poverty.Line + Unemployment.Rate +
    # Criminal Justice
    #Number.of.Criminal.Court.Judges + 
    Police.Officers.per.100.000.Residents, #+ Number.of.Full.Time.Prosecutors, 
  data   = rdf_FL,
  na.action = na.omit)
#summary(mod)
vif(mod3)


# OR
mod4 <- lm(
  car::logit(Public.Defender.conviction.rate) ~ 
    # Population
    Log.pop + Young.Males.Population + # Largest.Municipality.Population + 
    #High.School.Graduates +
    # Racial/Ethnicity
    African.American.Population + Native.American.Alaskan.Population + 
    Asian.or.Pacific.Islander.Population + Hispanic.or.Latino.Population +
    # Econ
    Below.Poverty.Line + Unemployment.Rate ,#+
    # Criminal Justice
    #Number.of.Criminal.Court.Judges +Police.Officers.per.100.000.Residents, + Number.of.Full.Time.Prosecutors, 
  data   = rdf_OR,
  na.action = na.omit)
#summary(mod)
vif(mod4)
```
```{r}

#PA
lm_pd_PA <- lm(
  car::logit(Public.Defender.conviction.rate) ~ 
    # Population
    Log.pop + Young.Males.Population + Largest.Municipality.Population + 
    # Racial/Ethnicity
    African.American.Population + Native.American.Alaskan.Population + 
    Asian.or.Pacific.Islander.Population + Hispanic.or.Latino.Population +
    # Econ
    Below.Poverty.Line + Unemployment.Rate +
    # Criminal Justice
    Number.of.Criminal.Court.Judges + Police.Officers.per.100.000.Residents + Number.of.Full.Time.Prosecutors, 
  data   = rdf_PA,
  na.action = na.omit)
#summary(lm_pd_PA)
vif(lm_pd_PA)

lm_p_PA <- lm(
  car::logit(Private.conviction.rate) ~ 
    # Population
    Log.pop + Young.Males.Population + Largest.Municipality.Population + 
    # Racial/Ethnicity
    African.American.Population + Native.American.Alaskan.Population + 
    Asian.or.Pacific.Islander.Population + Hispanic.or.Latino.Population +
    # Econ
    Below.Poverty.Line + Unemployment.Rate +
    # Criminal Justice
    Number.of.Criminal.Court.Judges + Police.Officers.per.100.000.Residents + Number.of.Full.Time.Prosecutors, 
  data   = rdf_PA,
  na.action = na.omit)
#summary(lm_p_PA)
vif(lm_p_PA)

lm_ca_PA <- lm(
  car::logit(Court.Appointed.conviction.rate) ~ 
    # Population
    Log.pop + Young.Males.Population + Largest.Municipality.Population +
    # Racial/Ethnicity
    African.American.Population + Native.American.Alaskan.Population + 
    Asian.or.Pacific.Islander.Population + Hispanic.or.Latino.Population +
    # Econ
    Below.Poverty.Line + Unemployment.Rate +
    # Criminal Justice
    Number.of.Criminal.Court.Judges + Police.Officers.per.100.000.Residents + Number.of.Full.Time.Prosecutors, 
  data   = rdf_PA,
  na.action = na.omit)
#summary(lm_ca_PA)
vif(lm_ca_PA)

lm_sr_PA <- lm(
  car::logit(Self.Represented.conviction.rate) ~ 
    # Population
    Log.pop + Young.Males.Population + Largest.Municipality.Population +
    # Racial/Ethnicity
    African.American.Population + Native.American.Alaskan.Population + 
    Asian.or.Pacific.Islander.Population + Hispanic.or.Latino.Population +
    # Econ
    Below.Poverty.Line + Unemployment.Rate +
    # Criminal Justice
    Number.of.Criminal.Court.Judges + Police.Officers.per.100.000.Residents + Number.of.Full.Time.Prosecutors, 
  data   = rdf_PA,
  na.action = na.omit)
#summary(lm_sr_PA)
vif(lm_sr_PA)
```

```{r, warning = FALSE, eval = FALSE}
# Selected som vars for visualization

rdf_PA %>%
  dplyr::select(Below.Poverty.Line, Public.Defender.conviction.rate, Private.conviction.rate,
                Court.Appointed.conviction.rate, Self.Represented.conviction.rate) %>%
  pivot_longer(-Below.Poverty.Line, names_to = "Type", values_to = "Rate") %>%
  ggplot(aes(x = Below.Poverty.Line, y = Rate)) +
  geom_point() +
  geom_smooth(method = "loess", se = TRUE, color = "red") +
  facet_wrap(~ Type, scales = "free_y") +
  labs(title = "Pennsylvania: Conviction Rate vs Poverty Rate",
       x = "Below Poverty Line", y = "Conviction Rate")
```

```{r}
# OR
lm_pd_OR<- lm(
  car::logit(Public.Defender.conviction.rate) ~ 
    # Population
    Log.pop + Young.Males.Population +
    # Racial/Ethnicity
    African.American.Population + Native.American.Alaskan.Population + 
    Asian.or.Pacific.Islander.Population + Hispanic.or.Latino.Population +
    # Econ
    Below.Poverty.Line + Unemployment.Rate ,
    # Criminal Justice
    # NONE
  data   = rdf_OR,
  na.action = na.omit)
#summary(lm_pd_OR)
vif(lm_pd_OR)

lm_p_OR<- lm(
  car::logit(Private.conviction.rate) ~ 
    # Population
    Log.pop + Young.Males.Population +
    # Racial/Ethnicity
    African.American.Population + Native.American.Alaskan.Population + 
    Asian.or.Pacific.Islander.Population + Hispanic.or.Latino.Population +
    # Econ
    Below.Poverty.Line + Unemployment.Rate ,
    # Criminal Justice
    # NONE
  data   = rdf_OR,
  na.action = na.omit)
#summary(lm_p_OR)
vif(lm_p_OR)


lm_ca_OR<- lm(
  car::logit(Court.Appointed.conviction.rate) ~ 
    # Population
    Log.pop + Young.Males.Population +
    # Racial/Ethnicity
    African.American.Population + Native.American.Alaskan.Population + 
    Asian.or.Pacific.Islander.Population + Hispanic.or.Latino.Population +
    # Econ
    Below.Poverty.Line + Unemployment.Rate ,
    # Criminal Justice
    # NONE
  data   = rdf_OR,
  na.action = na.omit)
#summary(lm_ca_OR)
vif(lm_ca_OR)


lm_sr_OR <- lm(
  car::logit(Self.Represented.conviction.rate) ~ 
    # Population
    Log.pop + Young.Males.Population +
    # Racial/Ethnicity
    African.American.Population + Native.American.Alaskan.Population + 
    Asian.or.Pacific.Islander.Population + Hispanic.or.Latino.Population +
    # Econ
    Below.Poverty.Line + Unemployment.Rate ,
    # Criminal Justice
    # NONE
  data   = rdf_OR,
  na.action = na.omit)
#summary(lm_sr_OR)
vif(lm_sr_OR)
```

```{r, warning = FALSE, eval = FALSE}
# Selected som vars for visualization

rdf_PA %>%
  dplyr::select(Log.pop, High.School.Graduates) %>%
  pivot_longer(-Log.pop, names_to = "Type", values_to = "Rate") %>%
  ggplot(aes(x = Log.pop, y = Rate)) +
  geom_point() +
  geom_smooth(method = "loess", se = TRUE, color = "red") +
  facet_wrap(~ Type, scales = "free_y") +
  labs(title = "Pennsylvania: Conviction Rate vs Log Population",
       x = "Log Population", y = "Conviction Rate")
```


```{r}
# FL
lm_pd_FL<- lm(
  car::logit(Public.Defender.conviction.rate) ~ 
    # Population
    Log.pop + Young.Males.Population + Largest.Municipality.Population + 
    # Racial/Ethnicity
    African.American.Population + Native.American.Alaskan.Population + 
    Asian.or.Pacific.Islander.Population + Hispanic.or.Latino.Population +
    # Econ
    Below.Poverty.Line + Unemployment.Rate +
    # Criminal Justice
    Police.Officers.per.100.000.Residents,
  data   = rdf_FL,
  na.action = na.omit)
#summary(lm_pd_FL)
vif(lm_pd_FL)

lm_p_FL <- lm(
  car::logit(Private.conviction.rate) ~ 
    # Population
    Log.pop + Young.Males.Population + Largest.Municipality.Population + 
    # Racial/Ethnicity
    African.American.Population + Native.American.Alaskan.Population + 
    Asian.or.Pacific.Islander.Population + Hispanic.or.Latino.Population +
    # Econ
    Below.Poverty.Line + Unemployment.Rate +
    # Criminal Justice
    Police.Officers.per.100.000.Residents,
  data   = rdf_FL,
  na.action = na.omit)
#summary(lm_p_FL)
vif(lm_p_FL)


lm_ca_FL<- lm(
  car::logit(Court.Appointed.conviction.rate) ~ 
    # Population
    Log.pop + Young.Males.Population + Largest.Municipality.Population + 
    # Racial/Ethnicity
    African.American.Population + Native.American.Alaskan.Population + 
    Asian.or.Pacific.Islander.Population + Hispanic.or.Latino.Population +
    # Econ
    Below.Poverty.Line + Unemployment.Rate +
    # Criminal Justice
    Police.Officers.per.100.000.Residents,
  data   = rdf_FL,
  na.action = na.omit)
#summary(lm_ca_FL)
vif(lm_ca_FL)

lm_sr_FL <- lm(
  car::logit(Self.Represented.conviction.rate) ~ 
    # Population
    Log.pop + Young.Males.Population + Largest.Municipality.Population + 
    # Racial/Ethnicity
    African.American.Population + Native.American.Alaskan.Population + 
    Asian.or.Pacific.Islander.Population + Hispanic.or.Latino.Population +
    # Econ
    Below.Poverty.Line + Unemployment.Rate +
    # Criminal Justice
    Police.Officers.per.100.000.Residents,
  data   = rdf_FL,
  na.action = na.omit)
#summary(lm_sr_FL)
vif(lm_sr_FL)
```


# Summary Tables
```{r, echo = TRUE}
summary(lm_pd_PA)
summary(lm_p_PA)
summary(lm_ca_PA)
summary(lm_sr_PA)

```
```{r, echo = TRUE}
summary(lm_pd_OR)
summary(lm_p_OR)
summary(lm_ca_OR)
summary(lm_sr_OR)

```
```{r, echo = TRUE}
summary(lm_pd_FL)
summary(lm_p_FL)
summary(lm_ca_FL)
summary(lm_sr_FL)
```

# Coefficient Tables
```{r, eval = FALSE}
library(stargazer)

state_coef_table <- function(state, lm_pd, lm_p, lm_cs, lm_sr, covar_labels) {
  stargazer(
    lm_pd,
    lm_p,
    lm_ca,
    lm_sr,
    
    type = "html",
    out = paste0(state, "_table.html"),
    
    dep.var.labels.include = FALSE,
    dep.var.caption = "",#Regression Results for Conviction Rates by Counsel Type (Pennsylvania)",
    column.labels = c(
      "Public Defender",
      "Private",
      "Court Appointed",
      "Self-Represented"
    ),
    
    #dep.var.labels = "Logit(Conviction Rate)",
    
    digits = 3,
    report = "vcstp",
    omit.stat = c("f", "adj.rsq"),
    covariate.labels = covar_labels,
    
    align = TRUE
  ) 
}


covar_labels_PA = c(
    "Log Population",
    "High School Graduates",
    "Log Urban Population",
    "Below Poverty Line",
    "Unemployment Rate",
    "Median Household Income",
    "Criminal Court Judges",
    "Full-Time Prosecutors",
    "Law Enforcement Agencies",
    "Part-Time Prosecutors",
    "Police per 100k"
  )

state_coef_table("pa", lm_pd_PA, lm_p_PA, lm_ca_PA, lm_sr_PA, covar_labels_PA)
#state_coef_table("fl", lm_pd_FL, lm_p_FL, lm_ca_FL, lm_sr_FL)
#state_coef_table("or", lm_pd_OR, lm_p_OR, lm_ca_OR, lm_sr_OR)
```

# PA Public Defender Residual Diagnostics
```{r, eval=FALSE}
# =========================
# Residual Diagnostics (PA - Public Defender)
# =========================

par(mfrow = c(2,2))

# 1. QQ plot (normality)
qqnorm(residuals(lm_pd_PA), main = "QQ Plot (PA - PD)")
qqline(residuals(lm_pd_PA), col = "red")

# 2. Residuals vs Fitted (linearity + homoskedasticity)
plot(fitted(lm_pd_PA), residuals(lm_pd_PA),
     main = "Residuals vs Fitted (PA - PD)",
     xlab = "Fitted Values", ylab = "Residuals")
abline(h = 0, col = "red")

# 3. Histogram of residuals
#hist(residuals(lm_pd_PA),
#     main = "Residual Histogram (PA - PD)",
#     xlab = "Residuals")

```

# Residual Disgnostics Function
```{r}
residual_diag_plots <- function (lm_att_state) {
  par(mfrow = c(2,2))
  qqnorm(residuals(lm_att_state), main = "QQ Plot")
  qqline(residuals(lm_att_state), col = "red")

  # 2. Residuals vs Fitted (linearity + homoskedasticity)
  plot(fitted(lm_att_state), residuals(lm_att_state),
       main = "Residuals vs Fitted",
       xlab = "Fitted Values", ylab = "Residuals")
  abline(h = 0, col = "red")
}

```
```{r, echo = TRUE}
residual_diag_plots(lm_pd_PA)
residual_diag_plots(lm_p_PA)
residual_diag_plots(lm_ca_PA)
residual_diag_plots(lm_sr_PA)

```
```{r, echo = TRUE}
residual_diag_plots(lm_pd_OR)
residual_diag_plots(lm_p_OR)
residual_diag_plots(lm_ca_OR)
residual_diag_plots(lm_sr_OR)

```
```{r, echo = TRUE}
residual_diag_plots(lm_pd_FL)
residual_diag_plots(lm_p_FL)
residual_diag_plots(lm_ca_FL)
residual_diag_plots(lm_sr_FL)
```

# PA Public Defender Leave-One-Out
```{r, eval=FALSE}
# =========================
# Leave-One-Out / Influence Analysis (PA - Public Defender)
# =========================

mod <- lm_pd_PA

# ---- Step 1: Identify outliers ----

# Studentized residuals (outliers in response)
rstud <- rstudent(mod)
outliers <- which(abs(rstud) > 2)

# Cook's distance (influential points)
cooks <- cooks.distance(mod)
threshold <- 4 / length(cooks)
influential <- which(cooks > threshold)

# Combine both
suspects <- unique(c(outliers, influential))

cat("Potential influential observations:\n")
print(suspects)

used_data <- model.frame(mod)
used_rows <- as.numeric(rownames(used_data))

suspect_info <- data.frame(
  obs = suspects,
  original_row = used_rows[suspects],
  location_id = rdf_PA$location_id[used_rows[suspects]],
  rstudent = round(rstud[suspects], 3),
  cooks_d = round(cooks[suspects], 3)
)
```

```{r, eval=FALSE}

# ---- Cook's Distance Plots ---#
# Cook's Distance Plot
plot(cooks,
     pch = 19,
     main = "Cook's Distance (PA Public Defender Model)",
     xlab = "Observation",
     ylab = "Cook's Distance")

abline(h = threshold, col = "red", lty = 2)

# label flagged points
text(suspects, cooks[suspects],
     labels = suspect_info$location_id,
     pos = 3, cex = 0.8)


# ---- Step 2: Leave-one-out refits ----

loo_models <- lapply(suspects, function(i) {
  lm(formula(mod), data = rdf_PA[-used_rows[i], , drop = FALSE],
     na.action = na.omit)
})

names(loo_models) <- paste0("remove_obs_", suspects)


# ---- Step 3: Compare coefficients ----

#original_coef <- coef(mod)

#cat("\nOriginal coefficients:\n")
#print(original_coef)

#cat("\nLeave-one-out coefficients:\n")
#print(lapply(loo_models, coef))


selected_indices <- seq_len(min(3, length(loo_models)))
selected_models <- loo_models[selected_indices]

```

```{r, eval=FALSE}
used_data <- model.frame(lm_pd_PA)
used_rows <- as.numeric(row.names(used_data))

suspect_info <- data.frame(
  obs = suspects, # row numbers in the model data
  location_id = rdf_PA$location_id[used_rows[suspects]],
  rstudent = rstud[suspects],
  cooks_d = cooks[suspects],
  row.names = NULL # row number in original dataset
)

suspect_info

vars_to_check <- c(
  "Log.pop",
  "Below.Poverty.Line",
  "Number.of.Criminal.Court.Judges"
)

# ---- Original coefficients ----
comparison_table <- data.frame(
  variable = vars_to_check,
  original = round(coef(lm_pd_PA)[vars_to_check], 3),
  row.names = NULL
)

# ---- Add LOO columns ----
for (j in seq_along(suspects)) {
  loc <- suspect_info$location_id[j]
  
  comparison_table[[paste0("remove_id_", loc)]] <- round(coef(loo_models[[j]])[vars_to_check], 3)
}

comparison_table


change_table <- data.frame(
  variable = vars_to_check
)

for (j in seq_along(suspects)) {
  loc <- suspect_info$location_id[j]
  
  change_table[[paste0("change_id_", loc)]] <-
    round(coef(loo_models[[j]])[vars_to_check] - coef(lm_pd_PA)[vars_to_check], 3) # LOO - Original
}

change_table

# reshape change_table to long format
change_long <- change_table %>%
  pivot_longer(-variable, names_to = "model", values_to = "change")

ggplot(change_long, aes(x = variable, y = change, fill = model)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(title = "Coefficient Changes After Removing Influential Observations",
       x = "Variable",
       y = "Change in Coefficient") +
  theme_minimal()
```

# Cook's Distanse Plot
```{r}
cooks_plot <- function (mod, state, counsel) {
  # ---- Step 1: Identify outliers ----
  
  # Studentized residuals (outliers in response)
  rstud <- rstudent(mod)
  outliers <- which(abs(rstud) > 2)
  
  # Cook's distance (influential points)
  cooks <- cooks.distance(mod)
  threshold <- 4 / length(cooks)
  influential <- which(cooks > threshold)
  
  # Combine both
  suspects <- unique(c(outliers, influential))
  
  #cat("Potential influential observations:\n")
  #print(suspects)
  
  used_data <- model.frame(mod)
  used_rows <- as.numeric(rownames(used_data))
  
  suspect_info <- data.frame(
    obs = suspects,
    original_row = used_rows[suspects],
    location_id = rdf_PA$location_id[used_rows[suspects]],
    rstudent = round(rstud[suspects], 3),
    cooks_d = round(cooks[suspects], 3)
  )
  # Cook's Distance Plot
  plot(cooks,
       pch = 19,
       #main = "Cook's Distance (PA Public Defender Model)",
       main = paste0("Cook's Distance (", state, " - ", counsel, ")"),
       xlab = "Observation",
       ylab = "Cook's Distance")
  
  abline(h = threshold, col = "red", lty = 2)
  
  # label flagged points
  text(suspects, cooks[suspects],
       labels = suspect_info$location_id,
       pos = 3, cex = 0.8)
}

```
```{r, echo = TRUE}
cooks_plot(lm_pd_PA, "PA", "PD")
cooks_plot(lm_p_PA, "PA", "P")
cooks_plot(lm_ca_PA, "PA", "CA")
cooks_plot(lm_sr_PA, "PA", "SR")

```
```{r, echo = TRUE}
cooks_plot(lm_pd_OR, "OR", "PD")
cooks_plot(lm_p_OR, "OR", "P")
cooks_plot(lm_ca_OR, "OR", "CA")
cooks_plot(lm_sr_OR, "OR", "SR")

```
```{r, echo = TRUE}
cooks_plot(lm_pd_FL, "FL", "PD")
cooks_plot(lm_p_FL, "FL", "P")
cooks_plot(lm_ca_FL, "FL", "CA")
cooks_plot(lm_sr_FL, "FL", "SR")
```


# Ignore below
```{r, eval=FALSE}
change_table <- data.frame(
  variable = vars_to_check
)

for (j in seq_along(suspects)) {
  loc <- suspect_info$location_id[j]
  
  change_table[[paste0("remove_id_", loc)]] <-
    round(
      coef(loo_models[[j]])[vars_to_check] - coef(mod)[vars_to_check],
      3
    )
}

rownames(change_table) <- NULL

change_table
```

```{r, eval=FALSE}
("Pennsylvania", "data-2009-2013.csv", "locations.csv")
pa_data <- read_csv("../../Data/raw/Pennsylvania_State_Data/data-2009-2013.csv")

convic_pa <- pa_data %>% filter(measure_id == 120) %>% select(value)
convic_pa
min(convic_pa, na.rm = TRUE)
```
