---
title: "Combined Regression & Diagnostics (Dirichlet + Conviction-Rate LMs)"
output: html_document
date: "2026-04-28"
---

Merged from:
- `Multinom_Regression_2.Rmd`  → Dirichlet model, `[DIR]` diagnostic plots, `[DIR]Regr_Table`
- `resids_loo.Rmd`              → Conviction-rate LMs, `[CR]` diagnostic plots

**Output naming convention** (matches `Appendix/` directory):

| Prefix | Plot | Location |
|--------|------|----------|
| `[DIR]` | Dirichlet diagnostics | `Appendix/{STATE}/` and `Appendix/{STATE}/{counsel}/` |
| `[CR]`  | Conviction-rate LM diagnostics | `Appendix/{STATE}/` and `Appendix/{STATE}/{counsel}/` |

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE, warning = FALSE, fig.align = "center",
                      echo = FALSE)
```

---

# Libraries & Data

```{r libs-and-data}
library(dplyr)
library(ggrepel)
library(stargazer)
library(tidyverse)
library(ggplot2)
library(tidyr)
library(bestglm)
library(car)
library(DirichletReg)

# ── Dirichlet data ──────────────────────────────────────────────────────────
FL_rep <- read.csv("../data/dir/full_resp_FL2.csv")
PA_rep <- read.csv("../data/dir/full_resp_PA2.csv")
OR_rep <- read.csv("../data/dir/full_resp_OR2.csv")

PA_rep <- PA_rep %>%
  mutate(Log.pop = log(Population)) %>%
  rename(
    private          = percent_p,
    public_defender  = percent_pd,
    appointed_counsel = percent_ca,
    self_represented = percent_sr,
    other            = percent_o,
    unknown          = percent_u
  ) %>%
  mutate(alternative = self_represented + other + unknown)

OR_rep <- OR_rep %>%
  mutate(Log.pop = log(Population)) %>%
  rename(
    private          = percent_p,
    public_defender  = percent_pd,
    appointed_counsel = percent_ca,
    self_represented = percent_sr,
    other            = percent_o,
    unknown          = percent_u
  ) %>%
  mutate(alternative = self_represented + other + unknown)

FL_rep <- FL_rep %>%
  mutate(Log.pop = log(Population)) %>%
  rename(
    private          = percent_p,
    public_defender  = percent_pd,
    appointed_counsel = percent_ca,
    self_represented = percent_sr,
    other            = percent_o,
    unknown          = percent_u
  ) %>%
  mutate(alternative = self_represented + other + unknown)

# ── Conviction-rate LM data ─────────────────────────────────────────────────
locations_pa <- read_csv("../data/raw/Pennsylvania_State_Data/locations.csv")
locations_or <- read_csv("../data/raw/Oregon_State_Data/locations-or.csv")
locations_fl <- read_csv("../data/raw/Florida_State_Data/locations-fl.csv")

rdf <- read.csv("../data/county_characteristics_conviction.csv")

rdf <- rdf %>%
  mutate(
    Log.pop = log(Population),
    Log.Largest.Municipality.Population = log(Largest.Municipality.Population + 1)
  )

rdf_PA <- rdf %>% filter(state == "PA") %>%
  left_join(locations_pa, by = c("location_id" = "id"))

rdf_OR <- rdf %>% filter(state == "OR") %>%
  left_join(locations_or, by = c("location_id" = "id"))

rdf_FL <- rdf %>% filter(state == "FL") %>%
  left_join(locations_fl, by = c("location_id" = "id"))
```

---

# Part 1 — Dirichlet Regression (`[DIR]`)

## Models

```{r dir-models}
PA_rep$Y <- DR_data(PA_rep[, c("private", "public_defender", "appointed_counsel", "alternative")])

mod_dir_PA <- DirichReg(Y ~
  Log.pop + Urban.Population +
  Below.Poverty.Line + Unemployment.Rate + Median.Household.Income + High.School.Graduates +
  African.American.Population,
  data = PA_rep)

OR_rep$Y <- DR_data(OR_rep[, c("private", "public_defender", "appointed_counsel", "alternative")])

mod_dir_OR <- DirichReg(Y ~
  Log.pop + Urban.Population +
  Below.Poverty.Line + Unemployment.Rate + High.School.Graduates,
  data = OR_rep)

FL_rep$Y <- DR_data(FL_rep[, c("private", "public_defender", "appointed_counsel", "alternative")])

mod_dir_FL <- DirichReg(Y ~
  Log.pop + Urban.Population +
  Below.Poverty.Line + Unemployment.Rate + Median.Household.Income + High.School.Graduates +
  African.American.Population,
  data = FL_rep)

summary(mod_dir_PA)
summary(mod_dir_OR)
summary(mod_dir_FL)
```

## Regression Tables → `[DIR]Regr_Table`

Saves one HTML regression table per state to `Appendix/{STATE}/[DIR]Regr_Table.html`.

```{r dir-regr-tables}
# Captures the console output of summary(model) and wraps it in a minimal
# self-contained HTML file.  DirichletReg stores its coefficient matrices
# inside the printed summary rather than in a cleanly-accessible list slot,
# so capturing the text output is the most robust approach.
save_dir_regr_table <- function(model, state_label, appendix_root = "Appendix") {
  out_dir  <- file.path(appendix_root, state_label)
  dir.create(out_dir, showWarnings = FALSE, recursive = TRUE)
  out_path <- file.path(out_dir, "[DIR]Regr_Table.html")

  # Capture the full printed summary as a character vector
  summary_text <- paste(capture.output(summary(model)), collapse = "\n")

  html <- sprintf('<!DOCTYPE html>
<html>
<head>
  <meta charset="UTF-8">
  <title>Dirichlet Regression Results — %s</title>
  <style>
    body { font-family: monospace; font-size: 13px; margin: 20px; background: #fff; }
    h2   { font-family: Arial, sans-serif; color: #3949ab; }
    pre  { background: #f5f5f5; padding: 16px; border-radius: 4px;
           border: 1px solid #ddd; white-space: pre; overflow-x: auto; }
    p.note { font-family: Arial, sans-serif; font-size: 11px; color: #555; }
  </style>
</head>
<body>
  <h2>Dirichlet Regression Results — %s</h2>
  <pre>%s</pre>
  <p class="note">Significance: *** p &lt; 0.001 &nbsp; ** p &lt; 0.01 &nbsp; * p &lt; 0.05 &nbsp; . p &lt; 0.1</p>
</body>
</html>',
  state_label, state_label,
  # Escape any HTML special characters in the summary text
  gsub("&", "&amp;",
    gsub("<", "&lt;",
      gsub(">", "&gt;", summary_text))))

  writeLines(html, out_path)
  message("Saved: ", out_path)
  invisible(out_path)
}

# --- Run for each state ---
save_dir_regr_table(mod_dir_PA, "PA")
save_dir_regr_table(mod_dir_OR, "OR")
save_dir_regr_table(mod_dir_FL, "FL")
```

## Diagnostic Plots → `[DIR]` files

Output paths (matching `Appendix/` naming convention):

| Plot | Output file |
|------|-------------|
| Residuals vs Fitted (all 4 categories) | `Appendix/{STATE}/[DIR]Resid_Fitted.png` |
| QQ Plots (all 4 categories)            | `Appendix/{STATE}/[DIR]QQ.png` |
| Fitted vs Observed (all 4 categories)  | `Appendix/{STATE}/[DIR]Fitted_Observed.png` |
| Fitted vs each predictor (per category)| `Appendix/{STATE}/{STATE}_4.5_fitted_vs_pred_{cat}.png` |

```{r dir-diagnostics-fn}
run_dirichlet_diagnostics <- function(model,
                                      data,
                                      predictors,
                                      state_label,
                                      appendix_root = "Appendix") {

  # Output directory is the state root, e.g. Appendix/PA
  out_dir <- file.path(appendix_root, state_label)
  dir.create(out_dir, showWarnings = FALSE, recursive = TRUE)

  response_cols <- c("private", "public_defender", "appointed_counsel", "alternative")

  resids <- residuals(model, type = "standardized")
  fits   <- fitted(model)
  n_cat  <- ncol(resids)
  n      <- nrow(fits)
  obs    <- as.matrix(data[seq_len(n), response_cols])

  save_base_plot <- function(file_name, plot_fn, width = 10, height = 8) {
    png(file.path(out_dir, file_name), width = width, height = height,
        units = "in", res = 150)
    plot_fn()
    dev.off()
    message("Saved: ", file.path(out_dir, file_name))
  }

  # 1. Standardized Residuals vs Fitted  →  [DIR]Resid_Fitted.png
  save_base_plot(
    "[DIR]Resid_Fitted.png",
    function() {
      par(mfrow = c(2, 2))
      for (i in seq_len(n_cat)) {
        plot(fits[, i], resids[, i],
             main = paste0(state_label, " - ", colnames(resids)[i]),
             xlab = "Fitted Values",
             ylab = "Standardized Residuals",
             pch  = 16, col = adjustcolor("steelblue", 0.6))
        abline(h = 0, lty = 2, col = "firebrick")
      }
    }
  )

  # 2. QQ Plots  →  [DIR]QQ.png
  save_base_plot(
    "[DIR]QQ.png",
    function() {
      par(mfrow = c(2, 2))
      for (i in seq_len(n_cat)) {
        qqnorm(resids[, i],
               main = paste0(state_label, " - ", colnames(resids)[i]),
               pch = 16, col = adjustcolor("steelblue", 0.6))
        qqline(resids[, i], col = "red", lwd = 2)
      }
    }
  )

  # 3. Fitted vs Observed  →  [DIR]Fitted_Observed.png
  save_base_plot(
    "[DIR]Fitted_Observed.png",
    function() {
      par(mfrow = c(2, 2))
      for (col in colnames(fits)) {
        plot(obs[, col], fits[, col],
             main = paste0(state_label, " - ", col),
             xlab = "Observed",
             ylab = "Fitted",
             pch  = 16, col = adjustcolor("steelblue", 0.6))
        abline(0, 1, col = "red", lty = 2, lwd = 2)
      }
    }
  )

  # 4. Residuals vs Each Predictor  (internal; not in Appendix naming convention)
  for (cat in colnames(resids)) {
    local({
      cat_ <- cat
      save_base_plot(
        paste0(state_label, "_4_resid_vs_pred_", cat_, ".png"),
        function() {
          par(mfrow = c(2, 2))
          for (pred in predictors) {
            x <- data[seq_len(n), pred]
            y <- resids[, cat_]
            complete <- complete.cases(x, y)
            plot(x[complete], y[complete],
                 main = paste0(state_label, ": ", cat_, " ~ ", pred),
                 xlab = pred,
                 ylab = "Standardized Residual",
                 pch  = 16, col = adjustcolor("steelblue", 0.6))
            abline(h = 0, lty = 2, col = "red")
            lines(lowess(x[complete], y[complete]), col = "darkgreen", lwd = 2)
          }
        },
        width = 8, height = 8
      )
    })
  }

  # 4.5 Fitted vs Each Predictor  →  {STATE}_4.5_fitted_vs_pred_{cat}.png
  for (cat in colnames(fits)) {
    local({
      cat_ <- cat
      save_base_plot(
        paste0(state_label, "_4.5_fitted_vs_pred_", cat_, ".png"),
        function() {
          par(mfrow = c(2, 2))
          for (pred in predictors) {
            x <- data[seq_len(n), pred]
            y <- fits[, cat_]
            complete <- complete.cases(x, y)
            plot(x[complete], y[complete],
                 main = paste0(state_label, ": ", cat_, " ~ ", pred),
                 xlab = pred,
                 ylab = "Fitted",
                 pch  = 16, col = adjustcolor("steelblue", 0.6))
            lines(lowess(x[complete], y[complete]), col = "darkgreen", lwd = 2)
          }
        },
        width = 8, height = 8
      )
    })
  }

  # 5. Leave-One-Out Influence  (internal; not in Appendix naming convention)
  coef_full     <- coef(model)
  model_formula <- formula(model)
  data_aligned  <- data[seq_len(n), ]

  influence <- sapply(seq_len(n), function(i) {
    tryCatch({
      mod_loo <- DirichReg(model_formula,
                           data    = data_aligned[-i, ],
                           model   = "alternative",
                           control = list(maxit = 5000))
      coef_loo <- coef(mod_loo)
      shared   <- intersect(names(coef_loo), names(coef_full))
      sum((coef_loo[shared] - coef_full[shared])^2)
    }, error   = function(e) NA,
       warning = function(w) NA)
  })

  cat(state_label, "- Successful LOO refits:", sum(!is.na(influence)), "out of", n, "\n")
  cat(state_label, "- Failed refits at observations:", which(is.na(influence)), "\n")

  if (sum(!is.na(influence)) > 2) {
    threshold <- mean(influence, na.rm = TRUE) + 2 * sd(influence, na.rm = TRUE)
    flagged   <- which(influence > threshold)
    loo_df    <- data.frame(obs = seq_len(n), influence = influence)

    p_loo <- ggplot(loo_df, aes(x = obs, y = influence)) +
      geom_segment(aes(xend = obs, yend = 0), color = "steelblue") +
      geom_hline(yintercept = threshold, color = "red", linetype = "dashed") +
      {
        if (length(flagged) > 0)
          ggrepel::geom_text_repel(data  = loo_df[flagged, ],
                                   aes(label = obs),
                                   color = "red", size = 3)
      } +
      labs(title = paste0(state_label, " - Leave-One-Out Influence"),
           x = "Observation", y = "LOO Influence") +
      theme_bw()

    out_path <- file.path(out_dir, paste0(state_label, "_5_loo_influence.png"))
    ggsave(out_path, plot = p_loo, width = 8, height = 5, dpi = 150)
    message("Saved: ", out_path)
  } else {
    cat(state_label, "- Too many failed LOO refits; LOO influence plot skipped.\n")
  }

  invisible(influence)
}
```

```{r dir-run-diagnostics}
predictors_PA <- c("Log.pop", "Urban.Population", "Unemployment.Rate", "Below.Poverty.Line")
predictors_OR <- c("Log.pop", "Urban.Population", "Unemployment.Rate", "Below.Poverty.Line")
predictors_FL <- c("Log.pop", "Urban.Population", "Unemployment.Rate", "Below.Poverty.Line")

run_dirichlet_diagnostics(mod_dir_PA, PA_rep, predictors_PA, "PA")
run_dirichlet_diagnostics(mod_dir_OR, OR_rep, predictors_OR, "OR")
run_dirichlet_diagnostics(mod_dir_FL, FL_rep, predictors_FL, "FL")
```

---

# Part 2 — Conviction-Rate Linear Models (`[CR]`)

## Models

```{r cr-models}
# ── Pennsylvania ────────────────────────────────────────────────────────────
lm_pd_PA <- lm(
  car::logit(Public.Defender.conviction.rate) ~
    Log.pop + Young.Males.Population +
    African.American.Population + Native.American.Alaskan.Population +
    Asian.or.Pacific.Islander.Population + Hispanic.or.Latino.Population +
    Below.Poverty.Line + Unemployment.Rate +
    Number.of.Criminal.Court.Judges + Police.Officers.per.100.000.Residents +
    Number.of.Full.Time.Prosecutors,
  data = rdf_PA, na.action = na.omit)

lm_p_PA <- lm(
  car::logit(Private.conviction.rate) ~
    Log.pop + Young.Males.Population +
    African.American.Population + Native.American.Alaskan.Population +
    Asian.or.Pacific.Islander.Population + Hispanic.or.Latino.Population +
    Below.Poverty.Line + Unemployment.Rate +
    Number.of.Criminal.Court.Judges + Police.Officers.per.100.000.Residents +
    Number.of.Full.Time.Prosecutors,
  data = rdf_PA, na.action = na.omit)

lm_ca_PA <- lm(
  car::logit(Court.Appointed.conviction.rate) ~
    Log.pop + Young.Males.Population +
    African.American.Population + Native.American.Alaskan.Population +
    Asian.or.Pacific.Islander.Population + Hispanic.or.Latino.Population +
    Below.Poverty.Line + Unemployment.Rate +
    Number.of.Criminal.Court.Judges + Police.Officers.per.100.000.Residents +
    Number.of.Full.Time.Prosecutors,
  data = rdf_PA, na.action = na.omit)

lm_sr_PA <- lm(
  car::logit(Self.Represented.conviction.rate) ~
    Log.pop + Young.Males.Population +
    African.American.Population + Native.American.Alaskan.Population +
    Asian.or.Pacific.Islander.Population + Hispanic.or.Latino.Population +
    Below.Poverty.Line + Unemployment.Rate +
    Number.of.Criminal.Court.Judges + Police.Officers.per.100.000.Residents +
    Number.of.Full.Time.Prosecutors,
  data = rdf_PA, na.action = na.omit)

# ── Oregon ───────────────────────────────────────────────────────────────────
lm_pd_OR <- lm(
  car::logit(Public.Defender.conviction.rate) ~
    Log.pop + Young.Males.Population +
    African.American.Population + Native.American.Alaskan.Population +
    Asian.or.Pacific.Islander.Population + Hispanic.or.Latino.Population +
    Below.Poverty.Line + Unemployment.Rate,
  data = rdf_OR, na.action = na.omit)

lm_p_OR <- lm(
  car::logit(Private.conviction.rate) ~
    Log.pop + Young.Males.Population +
    African.American.Population + Native.American.Alaskan.Population +
    Asian.or.Pacific.Islander.Population + Hispanic.or.Latino.Population +
    Below.Poverty.Line + Unemployment.Rate,
  data = rdf_OR, na.action = na.omit)

lm_ca_OR <- lm(
  car::logit(Court.Appointed.conviction.rate) ~
    Log.pop + Young.Males.Population +
    African.American.Population + Native.American.Alaskan.Population +
    Asian.or.Pacific.Islander.Population + Hispanic.or.Latino.Population +
    Below.Poverty.Line + Unemployment.Rate,
  data = rdf_OR, na.action = na.omit)

lm_sr_OR <- lm(
  car::logit(Self.Represented.conviction.rate) ~
    Log.pop + Young.Males.Population +
    African.American.Population + Native.American.Alaskan.Population +
    Asian.or.Pacific.Islander.Population + Hispanic.or.Latino.Population +
    Below.Poverty.Line + Unemployment.Rate,
  data = rdf_OR, na.action = na.omit)

# ── Florida ──────────────────────────────────────────────────────────────────
lm_pd_FL <- lm(
  car::logit(Public.Defender.conviction.rate) ~
    Log.pop + Young.Males.Population +
    African.American.Population + Native.American.Alaskan.Population +
    Asian.or.Pacific.Islander.Population + Hispanic.or.Latino.Population +
    Below.Poverty.Line + Unemployment.Rate +
    Police.Officers.per.100.000.Residents,
  data = rdf_FL, na.action = na.omit)

lm_p_FL <- lm(
  car::logit(Private.conviction.rate) ~
    Log.pop + Young.Males.Population +
    African.American.Population + Native.American.Alaskan.Population +
    Asian.or.Pacific.Islander.Population + Hispanic.or.Latino.Population +
    Below.Poverty.Line + Unemployment.Rate +
    Police.Officers.per.100.000.Residents,
  data = rdf_FL, na.action = na.omit)

lm_ca_FL <- lm(
  car::logit(Court.Appointed.conviction.rate) ~
    Log.pop + Young.Males.Population +
    African.American.Population + Native.American.Alaskan.Population +
    Asian.or.Pacific.Islander.Population + Hispanic.or.Latino.Population +
    Below.Poverty.Line + Unemployment.Rate +
    Police.Officers.per.100.000.Residents,
  data = rdf_FL, na.action = na.omit)

lm_sr_FL <- lm(
  car::logit(Self.Represented.conviction.rate) ~
    Log.pop + Young.Males.Population +
    African.American.Population + Native.American.Alaskan.Population +
    Asian.or.Pacific.Islander.Population + Hispanic.or.Latino.Population +
    Below.Poverty.Line + Unemployment.Rate +
    Police.Officers.per.100.000.Residents,
  data = rdf_FL, na.action = na.omit)
```

## Regression Plots → `[CR]Unemployment_LOESS` / `[CR]Unemployment_LIN`

```{r cr-reg-plots-fn}
reg_plots <- function(rdf_STATE, base_vals, state, lm_pd, lm_p, lm_ca, lm_sr) {

  u_seq    <- seq(min(rdf_STATE$Unemployment.Rate, na.rm = TRUE),
                  max(rdf_STATE$Unemployment.Rate, na.rm = TRUE),
                  length.out = 200)
  pred_grid <- base_vals[rep(1, length(u_seq)), ]
  pred_grid$Unemployment.Rate <- u_seq

  make_pred_df <- function(model, label, newdata) {
    pred <- predict(model, newdata = newdata, se.fit = TRUE)
    newdata %>%
      mutate(
        fit_link  = pred$fit,
        se_link   = pred$se.fit,
        fit       = plogis(fit_link),
        lwr       = plogis(fit_link - 1.96 * se_link),
        upr       = plogis(fit_link + 1.96 * se_link),
        Attorney.Type = label
      )
  }

  plot_df <- bind_rows(
    make_pred_df(lm_pd, "Public Defender",  pred_grid),
    make_pred_df(lm_p,  "Private Counsel",  pred_grid),
    make_pred_df(lm_ca, "Court Appointed",  pred_grid),
    make_pred_df(lm_sr, "Self-Represented", pred_grid)
  )

  points_df <- rdf_STATE %>%
    select(Unemployment.Rate,
           Private.conviction.rate, Public.Defender.conviction.rate,
           Court.Appointed.conviction.rate, Self.Represented.conviction.rate) %>%
    pivot_longer(cols = -Unemployment.Rate,
                 names_to = "Attorney.Type", values_to = "conviction_rate") %>%
    mutate(
      Attorney.Type = dplyr::recode(Attorney.Type,
        "Private.conviction.rate"        = "Private Counsel",
        "Public.Defender.conviction.rate" = "Public Defender",
        "Court.Appointed.conviction.rate" = "Court Appointed",
        "Self.Represented.conviction.rate" = "Self-Represented"),
      conviction_rate = conviction_rate / 100
    )

  loess_plt <- ggplot(plot_df, aes(x = Unemployment.Rate, y = fit)) +
    geom_ribbon(aes(ymin = lwr, ymax = upr), alpha = 0.2) +
    geom_smooth(method = "loess", se = FALSE, color = "red", linewidth = 1) +
    geom_point(data = points_df, aes(x = Unemployment.Rate, y = conviction_rate),
               alpha = 0.6, size = 2) +
    facet_wrap(~ Attorney.Type, ncol = 2) +
    labs(title = paste0("Predicted Conviction Rate vs. Unemployment Rate in ", state, " — LOESS"),
         x = "Unemployment Rate", y = "Predicted Conviction Rate") +
    theme_minimal(base_size = 12)

  linear_plt <- ggplot(plot_df, aes(x = Unemployment.Rate, y = fit)) +
    geom_ribbon(aes(ymin = lwr, ymax = upr), alpha = 0.2) +
    geom_line(linewidth = 1, color = "red") +
    geom_point(data = points_df, aes(x = Unemployment.Rate, y = conviction_rate),
               alpha = 0.6, size = 2) +
    facet_wrap(~ Attorney.Type, ncol = 2) +
    labs(title = paste0("Predicted Conviction Rate vs. Unemployment Rate in ", state, " Linear"),
         x = "Unemployment Rate", y = "Predicted Conviction Rate") +
    theme_minimal(base_size = 12)

  list(loess_plt = loess_plt, linear_plt = linear_plt)
}
```

```{r cr-base-vals}
base_vals_PA <- rdf_PA %>%
  summarise(
    Log.pop = mean(Log.pop, na.rm = TRUE),
    Young.Males.Population = mean(Young.Males.Population, na.rm = TRUE),
    African.American.Population = mean(African.American.Population, na.rm = TRUE),
    Native.American.Alaskan.Population = mean(Native.American.Alaskan.Population, na.rm = TRUE),
    Asian.or.Pacific.Islander.Population = mean(Asian.or.Pacific.Islander.Population, na.rm = TRUE),
    Hispanic.or.Latino.Population = mean(Hispanic.or.Latino.Population, na.rm = TRUE),
    Below.Poverty.Line = mean(Below.Poverty.Line, na.rm = TRUE),
    Number.of.Criminal.Court.Judges = mean(Number.of.Criminal.Court.Judges, na.rm = TRUE),
    Police.Officers.per.100.000.Residents = mean(Police.Officers.per.100.000.Residents, na.rm = TRUE),
    Number.of.Full.Time.Prosecutors = mean(Number.of.Full.Time.Prosecutors, na.rm = TRUE)
  )

base_vals_OR <- rdf_OR %>%
  summarise(
    Log.pop = mean(Log.pop, na.rm = TRUE),
    Young.Males.Population = mean(Young.Males.Population, na.rm = TRUE),
    African.American.Population = mean(African.American.Population, na.rm = TRUE),
    Native.American.Alaskan.Population = mean(Native.American.Alaskan.Population, na.rm = TRUE),
    Asian.or.Pacific.Islander.Population = mean(Asian.or.Pacific.Islander.Population, na.rm = TRUE),
    Hispanic.or.Latino.Population = mean(Hispanic.or.Latino.Population, na.rm = TRUE),
    Below.Poverty.Line = mean(Below.Poverty.Line, na.rm = TRUE)
  )

base_vals_FL <- rdf_FL %>%
  summarise(
    Log.pop = mean(Log.pop, na.rm = TRUE),
    Young.Males.Population = mean(Young.Males.Population, na.rm = TRUE),
    African.American.Population = mean(African.American.Population, na.rm = TRUE),
    Native.American.Alaskan.Population = mean(Native.American.Alaskan.Population, na.rm = TRUE),
    Asian.or.Pacific.Islander.Population = mean(Asian.or.Pacific.Islander.Population, na.rm = TRUE),
    Hispanic.or.Latino.Population = mean(Hispanic.or.Latino.Population, na.rm = TRUE),
    Below.Poverty.Line = mean(Below.Poverty.Line, na.rm = TRUE),
    Police.Officers.per.100.000.Residents = mean(Police.Officers.per.100.000.Residents, na.rm = TRUE)
  )
```

Output: `Appendix/{STATE}/[CR]Unemployment_LOESS.png` and `[CR]Unemployment_LIN.png`

```{r cr-save-reg-plots}
save_reg_plots <- function(state_label, rdf_STATE, base_vals,
                           state_name, lm_pd, lm_p, lm_ca, lm_sr,
                           appendix_root = "Appendix") {
  out_dir <- file.path(appendix_root, state_label)
  dir.create(out_dir, showWarnings = FALSE, recursive = TRUE)

  plts <- reg_plots(rdf_STATE, base_vals, state_name, lm_pd, lm_p, lm_ca, lm_sr)

  ggsave(file.path(out_dir, "[CR]Unemployment_LOESS.png"),
         plot = plts$loess_plt, width = 10, height = 8, dpi = 150)
  message("Saved: ", file.path(out_dir, "[CR]Unemployment_LOESS.png"))

  ggsave(file.path(out_dir, "[CR]Unemployment_LIN.png"),
         plot = plts$linear_plt, width = 10, height = 8, dpi = 150)
  message("Saved: ", file.path(out_dir, "[CR]Unemployment_LIN.png"))
}

save_reg_plots("PA", rdf_PA, base_vals_PA, "Pennsylvania",
               lm_pd_PA, lm_p_PA, lm_ca_PA, lm_sr_PA)
save_reg_plots("OR", rdf_OR, base_vals_OR, "Oregon",
               lm_pd_OR, lm_p_OR, lm_ca_OR, lm_sr_OR)
save_reg_plots("FL", rdf_FL, base_vals_FL, "Florida",
               lm_pd_FL, lm_p_FL, lm_ca_FL, lm_sr_FL)
```

## Coefficient Tables → `[CR]Regr_Table`

Output: `Appendix/{STATE}/[CR]Regr_Table.html`

```{r cr-coef-tables}
covar_labels_PA <- c(
  "Log Population", "Proportion of Young Males",
  "Proportion African American", "Proportion Native American / Alaskan",
  "Proportion Asian / Pacific Islander", "Proportion Hispanic or Latino",
  "Poverty Rate", "Unemployment Rate",
  "Number of Criminal Court Judges", "Police Officers per 100,000 Residents",
  "Number of Full-Time Prosecutors"
)

covar_labels_OR <- c(
  "Log Population", "Proportion of Young Males",
  "Proportion African American", "Proportion Native American / Alaskan",
  "Proportion Asian / Pacific Islander", "Proportion Hispanic or Latino",
  "Poverty Rate", "Unemployment Rate"
)

covar_labels_FL <- c(
  "Log Population", "Proportion of Young Males",
  "Proportion African American", "Proportion Native American / Alaskan",
  "Proportion Asian / Pacific Islander", "Proportion Hispanic or Latino",
  "Poverty Rate", "Unemployment Rate",
  "Police Officers per 100,000 Residents"
)

save_cr_regr_table <- function(state_label, lm_pd, lm_p, lm_ca, lm_sr,
                               covar_labels, state_name,
                               appendix_root = "Appendix") {
  out_dir  <- file.path(appendix_root, state_label)
  dir.create(out_dir, showWarnings = FALSE, recursive = TRUE)
  out_path <- file.path(out_dir, "[CR]Regr_Table.html")

  stargazer(
    lm_pd, lm_p, lm_ca, lm_sr,
    type             = "html",
    out              = out_path,
    title            = paste0("Conviction Rate Regression Results by Attorney Type (", state_name, ")"),
    dep.var.labels.include = FALSE,
    dep.var.caption  = "",
    column.labels    = c("Public Defender", "Private", "Court Appointed", "Self-Represented"),
    digits           = 3,
    report           = "vc*s",
    omit.stat        = c("f", "rsq", "ser"),
    covariate.labels = covar_labels,
    align            = TRUE
  )
  message("Saved: ", out_path)
}

save_cr_regr_table("PA", lm_pd_PA, lm_p_PA, lm_ca_PA, lm_sr_PA,
                   covar_labels_PA, "Pennsylvania")
save_cr_regr_table("OR", lm_pd_OR, lm_p_OR, lm_ca_OR, lm_sr_OR,
                   covar_labels_OR, "Oregon")
save_cr_regr_table("FL", lm_pd_FL, lm_p_FL, lm_ca_FL, lm_sr_FL,
                   covar_labels_FL, "Florida")
```

## Residual Diagnostics → `[CR]QQ_Resid` / `[CR]Cooks`

Output per counsel type: `Appendix/{STATE}/{counsel}/[CR]QQ_Resid.png`
and `Appendix/{STATE}/{counsel}/[CR]Cooks.png`

```{r cr-diag-fns}
# QQ + Residuals vs Fitted (2-panel base plot) --------------------------------
residual_diag_plots <- function(lm_att_state) {
  par(mfrow = c(2, 1))
  qqnorm(residuals(lm_att_state), main = "QQ Plot")
  qqline(residuals(lm_att_state), col = "red")
  plot(fitted(lm_att_state), residuals(lm_att_state),
       main = "Residuals vs Fitted",
       xlab = "Fitted Values", ylab = "Residuals")
  abline(h = 0, col = "red")
}

# Cook's Distance ggplot -------------------------------------------------------
cooks_plot <- function(mod, state, counsel, rdf_STATE) {
  rstud       <- rstudent(mod)
  cooks       <- cooks.distance(mod)
  threshold   <- 4 / length(cooks)
  influential <- which(cooks > threshold)
  used_rows   <- as.numeric(rownames(model.frame(mod)))

  df <- data.frame(
    obs   = seq_along(cooks),
    cooks = cooks,
    label = rdf_STATE$name[used_rows]
  )

  ggplot(df, aes(x = obs, y = cooks)) +
    geom_point(color = "grey70") +
    geom_hline(yintercept = threshold, color = "red", linetype = "dashed") +
    geom_text_repel(data = df[influential, ], aes(label = label), size = 3) +
    labs(
      title = paste0("Cook's Distance (", state, " - ", counsel, ") conviction rate"),
      x = "Observation", y = "Cook's Distance"
    ) +
    theme_minimal() +
    theme(axis.text.x = element_blank(), axis.ticks.x = element_blank())
}

# Wrapper: save both plots for one state/counsel combination ------------------
# counsel_code: "PD", "P", "AC", "SR"  (matches Appendix sub-folder names)
save_cr_diagnostics <- function(mod, state_label, counsel_code, rdf_STATE,
                                appendix_root = "Appendix") {
  out_dir <- file.path(appendix_root, state_label, counsel_code)
  dir.create(out_dir, showWarnings = FALSE, recursive = TRUE)

  # QQ + Resid vs Fitted  →  [CR]QQ_Resid.png
  png(file.path(out_dir, "[CR]QQ_Resid.png"), width = 10, height = 8,
      units = "in", res = 150)
  residual_diag_plots(mod)
  dev.off()
  message("Saved: ", file.path(out_dir, "[CR]QQ_Resid.png"))

  # Cook's Distance  →  [CR]Cooks.png
  p_cooks <- cooks_plot(mod, state_label, counsel_code, rdf_STATE)
  ggsave(file.path(out_dir, "[CR]Cooks.png"),
         plot = p_cooks, width = 8, height = 5, dpi = 150)
  message("Saved: ", file.path(out_dir, "[CR]Cooks.png"))
}
```

```{r cr-save-diagnostics}
# Pennsylvania
save_cr_diagnostics(lm_pd_PA, "PA", "PD", rdf_PA)
save_cr_diagnostics(lm_p_PA,  "PA", "P",  rdf_PA)
save_cr_diagnostics(lm_ca_PA, "PA", "AC", rdf_PA)
save_cr_diagnostics(lm_sr_PA, "PA", "SR", rdf_PA)

# Oregon
save_cr_diagnostics(lm_pd_OR, "OR", "PD", rdf_OR)
save_cr_diagnostics(lm_p_OR,  "OR", "P",  rdf_OR)
save_cr_diagnostics(lm_ca_OR, "OR", "AC", rdf_OR)
save_cr_diagnostics(lm_sr_OR, "OR", "SR", rdf_OR)

# Florida
save_cr_diagnostics(lm_pd_FL, "FL", "PD", rdf_FL)
save_cr_diagnostics(lm_p_FL,  "FL", "P",  rdf_FL)
save_cr_diagnostics(lm_ca_FL, "FL", "AC", rdf_FL)
save_cr_diagnostics(lm_sr_FL, "FL", "SR", rdf_FL)
```

---

# OR — Private (Outliers Removed)
Removed all counties with Cook's distance above the threshold.

```{r or-private-clean}
cooks_p_OR      <- cooks.distance(lm_p_OR)
threshold_p_OR  <- 4 / length(cooks_p_OR)
influential_p_OR <- which(cooks_p_OR > threshold_p_OR)
used_data_p_OR  <- model.frame(lm_p_OR)
used_rows_p_OR  <- as.numeric(rownames(used_data_p_OR))

rdf_OR_clean_p_OR <- rdf_OR[-used_rows_p_OR[influential_p_OR], ]

lm_p_OR_clean <- lm(
  car::logit(Private.conviction.rate) ~
    Log.pop + Young.Males.Population +
    African.American.Population + Native.American.Alaskan.Population +
    Asian.or.Pacific.Islander.Population + Hispanic.or.Latino.Population +
    Below.Poverty.Line + Unemployment.Rate,
  data = rdf_OR_clean_p_OR, na.action = na.omit)

residual_diag_plots(lm_p_OR_clean)
cooks_plot(lm_p_OR_clean, "OR", "P -- w/out influential", rdf_OR_clean_p_OR)
summary(lm_p_OR_clean)
```

# OR — Private (Multnomah Removed)

```{r or-private-clean2}
max_influential         <- which.max(cooks_p_OR)
rdf_OR_clean2_p_OR      <- rdf_OR[-used_rows_p_OR[max_influential], ]

lm_p_OR_clean2 <- lm(
  car::logit(Private.conviction.rate) ~
    Log.pop + Young.Males.Population +
    African.American.Population + Native.American.Alaskan.Population +
    Asian.or.Pacific.Islander.Population + Hispanic.or.Latino.Population +
    Below.Poverty.Line + Unemployment.Rate,
  data = rdf_OR_clean_p_OR, na.action = na.omit)

residual_diag_plots(lm_p_OR_clean2)
cooks_plot(lm_p_OR_clean2, "OR", "P -- w/out Multnomah", rdf_OR_clean2_p_OR)
summary(lm_p_OR_clean2)
```
