---
title: "Dirichlet Regression"
output: pdf_document
date: "2026-04-24"
---
Adapted from Zining
Changes
- Using Urban.Population instead of Urban.Population (why are we logging a percent)
- Renamed to more descriptive names
- Deleted alternative models section

| Factor                       | PA | OR | FL |
|------------------------------|----|----|----|
| Log.pop (Pop)                | 1  | 1  | 1  |
| Urban.Population  (Pop)      | 1  | 1  | 1  |
| Below.Poverty.Line  (Econ)   | 1  | 1  | 1  |
| Unemployment.Rate   (Econ)   | 1  | 1  | 1  |
| High.School.Graduates (Econ) | 1  | 1  | 1  |
| Median.Household.Income(Econ)| 1  | 0  | 1  |
| African.American.Population  | 0  | 0  | 1  |

```{r setup, include=FALSE}
#knitr::opts_chunk$set(echo = TRUE, tidy = TRUE, tidy.opts = list(width.cutoff = 60))

knitr::opts_chunk$set(message=FALSE, warning=FALSE, fig.align="center",
               echo=FALSE)
```

```{r Libs and Data}
library(dplyr)
library(ggrepel)
library(stargazer)
library(tidyverse)
library(ggplot2)
library(tidyr)

library(bestglm)
library(stargazer)
library(car)

library(DirichletReg)

FL_rep <- read.csv("full_resp_FL2.csv")
PA_rep <- read.csv("full_resp_PA2.csv")
OR_rep <- read.csv("full_resp_OR2.csv")

PA_rep <- PA_rep %>% 
  mutate(Log.pop = log(Population)) %>%
  rename(
    private = percent_p,
    public_defender = percent_pd,
    appointed_counsel = percent_ca,
    self_represented = percent_sr,
    other = percent_o,
    unknown = percent_u
  ) %>%
  mutate(alternative = self_represented + other + unknown)

OR_rep <- OR_rep %>% 
  mutate(Log.pop = log(Population)) %>%
  rename(
    private = percent_p,
    public_defender = percent_pd,
    appointed_counsel = percent_ca,
    self_represented = percent_sr,
    other = percent_o,
    unknown = percent_u
  )%>%
  mutate(alternative = self_represented + other + unknown)

FL_rep <- FL_rep %>% 
  mutate(Log.pop = log(Population)) %>%
  rename(
    private = percent_p,
    public_defender = percent_pd,
    appointed_counsel = percent_ca,
    self_represented = percent_sr,
    other = percent_o,
    unknown = percent_u
  )%>%
  mutate(alternative = self_represented + other + unknown)
```
# Default Model 

```{r Models}
PA_rep$Y <- DR_data(PA_rep[, c("private", "public_defender", "appointed_counsel", "alternative")])

mod_dir_PA <- DirichReg(Y ~
    Log.pop + Urban.Population +
    Below.Poverty.Line + Unemployment.Rate + Median.Household.Income + High.School.Graduates +
    African.American.Population,
    data = PA_rep)

OR_rep$Y <- DR_data(OR_rep[, c("private", "public_defender", "appointed_counsel", "alternative")])

mod_dir_OR <- DirichReg(Y ~
    Log.pop + Urban.Population +
    Below.Poverty.Line + Unemployment.Rate + High.School.Graduates,
    data = OR_rep)

FL_rep$Y <- DR_data(FL_rep[, c("private", "public_defender", "appointed_counsel", "alternative")])

mod_dir_FL <- DirichReg(Y ~
    Log.pop + Urban.Population +
    Below.Poverty.Line + Unemployment.Rate + Median.Household.Income + High.School.Graduates +
    African.American.Population,
    data = FL_rep)

summary(mod_dir_PA)
summary(mod_dir_OR)
summary(mod_dir_FL)
```

```{r Diagnostics Fn}
run_dirichlet_diagnostics <- function(model,
                                      data,
                                      predictors,
                                      state_label,
                                      out_dir = "diagnostics") {

  dir.create(out_dir, showWarnings = FALSE, recursive = TRUE)

  response_cols <- c("private", "public_defender", "appointed_counsel",
                     "self_represented", "other", "unknown")

  resids <- residuals(model, type = "standardized")
  fits   <- fitted(model)
  n_cat  <- ncol(resids)
  n      <- nrow(fits)
  obs    <- as.matrix(data[seq_len(n), response_cols])  # positional alignment

  # helper: plot_fn is a function() so it executes inside the png device
  save_base_plot <- function(file_name, plot_fn, width = 10, height = 8) {
    png(file.path(out_dir, file_name), width = width, height = height,
        units = "in", res = 150)
    plot_fn()
    dev.off()
    message("Saved: ", file.path(out_dir, file_name))
  }

  # 1. Standardized Residuals vs Fitted
  save_base_plot(
    paste0(state_label, "_1_resid_vs_fitted.png"),
    function() {
      par(mfrow = c(2, 2))
      for (i in seq_len(n_cat)) {
        plot(fits[, i], resids[, i],
             main = paste0(state_label, " - ", colnames(resids)[i]),
             xlab = "Fitted Values",
             ylab = "Standardized Residuals",
             pch  = 16, col = adjustcolor("steelblue", 0.6))
        abline(h =  0, lty = 2, col = "firebrick")
      }
    }
  )

  # 2. QQ Plots
  save_base_plot(
    paste0(state_label, "_2_qq_plots.png"),
    function() {
      par(mfrow = c(2, 2))
      for (i in seq_len(n_cat)) {
        qqnorm(resids[, i],
               main = paste0(state_label, " - ", colnames(resids)[i]),
               pch = 16, col = adjustcolor("steelblue", 0.6))
        qqline(resids[, i], col = "red", lwd = 2)
      }
    }
  )

  # 3. Fitted vs Observed
  save_base_plot(
    paste0(state_label, "_3_fitted_vs_observed.png"),
    function() {
      par(mfrow = c(2, 2))
      for (col in colnames(fits)) {
        plot(obs[, col], fits[, col],
             main = paste0(state_label, " - ", col),
             xlab = "Observed",
             ylab = "Fitted",
             pch  = 16, col = adjustcolor("steelblue", 0.6))
        abline(0, 1, col = "red", lty = 2, lwd = 2)
      }
    }
  )

# 4. Residuals vs Each Predictor
# Layout hard-coded to (2, 2) for up to 4 predictors
for (cat in colnames(resids)) {
  local({
    cat_ <- cat
    save_base_plot(
      paste0(state_label, "_4_resid_vs_pred_", cat_, ".png"),
      function() {
        par(mfrow = c(2, 2))
        for (pred in predictors) {
          x <- data[seq_len(n), pred]
          y <- resids[, cat_]
          complete <- complete.cases(x, y)
          x_clean  <- x[complete]
          y_clean  <- y[complete]

          plot(x_clean, y_clean,
               main = paste0(state_label, ": ", cat_, " ~ ", pred),
               xlab = pred,
               ylab = "Standardized Residual",
               pch  = 16, col = adjustcolor("steelblue", 0.6))
          abline(h = 0, lty = 2, col = "red")
          lines(lowess(x_clean, y_clean), col = "darkgreen", lwd = 2)
        }
      },
      width  = 8,
      height = 8
    )
  })
}

  # 5. Leave-One-Out Influence
  coef_full     <- coef(model)
  model_formula <- formula(model)
  data_aligned  <- data[seq_len(n), ]

  influence <- sapply(seq_len(n), function(i) {
    tryCatch({
      mod_loo <- DirichReg(model_formula,
                           data    = data_aligned[-i, ],
                           model   = "alternative",
                           control = list(maxit = 5000))
      coef_loo <- coef(mod_loo)
      shared   <- intersect(names(coef_loo), names(coef_full))
      sum((coef_loo[shared] - coef_full[shared])^2)
    }, error   = function(e) NA,
       warning = function(w) NA)
  })

  cat(state_label, "- Successful LOO refits:", sum(!is.na(influence)),
      "out of", n, "\n")
  cat(state_label, "- Failed refits at observations:",
      which(is.na(influence)), "\n")

  if (sum(!is.na(influence)) > 2) {

    threshold <- mean(influence, na.rm = TRUE) + 2 * sd(influence, na.rm = TRUE)
    flagged   <- which(influence > threshold)

    loo_df <- data.frame(obs = seq_len(n), influence = influence)

    p_loo <- ggplot(loo_df, aes(x = obs, y = influence)) +
      geom_segment(aes(xend = obs, yend = 0), color = "steelblue") +
      geom_hline(yintercept = threshold, color = "red", linetype = "dashed") +
      {
        if (length(flagged) > 0)
          ggrepel::geom_text_repel(data  = loo_df[flagged, ],
                                   aes(label = obs),
                                   color = "red", size = 3)
      } +
      labs(title = paste0(state_label, " - Leave-One-Out Influence"),
           x = "Observation", y = "LOO Influence") +
      theme_bw()

    out_path <- file.path(out_dir, paste0(state_label, "_5_loo_influence.png"))
    ggsave(out_path, plot = p_loo, width = 8, height = 5, dpi = 150)
    message("Saved: ", out_path)

  } else {
    cat(state_label, "- Too many failed LOO refits; LOO influence plot skipped.\n")
  }

  invisible(influence)
}
```

```{r Run Diagnostics}
run_dirichlet_diagnostics(mod_dir_PA, 
                          PA_rep,  c("Log.pop","Urban.Population","Unemployment.Rate","Below.Poverty.Line"),
                          "PA", 
                          "Diagnostic_Plots/PA_Alt")

run_dirichlet_diagnostics(mod_dir_OR, 
                          OR_rep,  c("Log.pop","Urban.Population","Unemployment.Rate","Below.Poverty.Line"),
                          "OR", 
                          "Diagnostic_Plots/OR_Alt")

run_dirichlet_diagnostics(mod_dir_FL, 
                          FL_rep,  c("Log.pop","Urban.Population","Unemployment.Rate","Below.Poverty.Line"),
                          "FL", 
                          "Diagnostic_Plots/FL_Alt")
```